Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2013-11-19 paper/paper.tex
remove answered davidsays and recolor Rene blue Tested everything on collins.

\newcommand{\fixme}[1]{\red{[#1]}}
\newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
\newcommand{\renesays}[1]{{\color{red} [\green{Rene:} \emph{#1}]}}

@@

In order to address the limits at which the stability of the
oscillations of the Min system break down, as observed by Mannik
\emph{et al.}~\cite{mannik2012robustness}, we model the Min system in
a variety of cell shapes.  We begin with natural pill-shaped cells,
and the proceed to examine a number of flattened pancake-like shapes,
which reflect the experiment of Mannik \emph{et al.}, in which
bacteria were confined within a thin slit~\cite{mannik2012robustness}.
Our pill shapes differ from those of Huang \emph{et al.} in that they
are cylinders with hemisphere endcaps instead of pure cylindridrical
shapes. \davidsays{Double-check the Huang paper on their shapes.}  Our
cylinderidrical radius is $0.50\micron$ and the lengths of our cells
(measured between the tips of the endcaps) are $5\micron$, $4\micron$, $3\micron$,
and $2.5\micron$.

>>>>

\newcommand{\fixme}[1]{\red{[#1]}}
\newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
\newcommand{\renesays}[1]{{\color{red} [\blue{Rene:} \emph{#1}]}}

@@

In order to address the limits at which the stability of the
oscillations of the Min system break down, as observed by Mannik
\emph{et al.}~\cite{mannik2012robustness}, we model the Min system in
a variety of cell shapes.  We begin with natural pill-shaped cells,
and the proceed to examine a number of flattened pancake-like shapes,
which reflect the experiment of Mannik \emph{et al.}, in which
bacteria were confined within a thin slit~\cite{mannik2012robustness}.
Our pill shapes differ from those of Huang \emph{et al.} in that they
are cylinders with hemisphere endcaps instead of pure cylindridrical
shapes.  Our
cylinderidrical radius is $0.50\micron$ and the lengths of our cells
(measured between the tips of the endcaps) are $5\micron$, $4\micron$, $3\micron$,
and $2.5\micron$.
